---
title: 'Lab 7: Multiple linear regression into'
author: "Alia Ajina"
date: "11/9/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(modelsummary)
library(stargazer)
```

## Explore penguins

Use `GGally::ggpairs()` to create pairs plot.

```{r}
ggpairs(penguins)
```

That's kind of overkill. Let's simplify the variables that we include in our ggpairs plot:

- species
- bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

Quick way to look at multi-variable comparisons and add some groupings ^^

## Multiple linear regression

We are going to try to understand (a bit better) relationships between multiple predictor variables and an outcome which is penguin body mass.

The different predcitor variables we're going to try are:

- species
- flipper length
- sex
- bill depth

They should be grounded in some understanding of the impacts of these different variables on body mass but we're just going to try some different options

### Model 1

Model body mass based on only flipper length and bill depth (bad idea... there are important variables missing, ie sex)

(a model running is not a good indication of success for modeling)

(tilde = as a function of...)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Call model by name to return only coefficients:
model_1

summary(model_1)
```
If everything else is held constant, on average, for each 1 mm increase in flipper length, we expect a 51.54 (`r model_1$flipper_length_mm` <- this is WRONG, figure it out, may be why she uses tidy data) grams increase in body mass.

or "If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass is expected to increase by 51.54 g, on average." <- remember to use inline code

R squared means "76% of variance in penguin body mass (dependent variable), is explained by this model (or the independent variables, which are flipper length and bill length)"

There is still 24% that is not explained, might be missing some important variables (such as species or sex) that explain remaining variance.

Actually -- we think that a model for penguin body mass should contain variable species, flipper length, and penguin sex.

```{r}
model_2 <- lm(body_mass_g ~ species + flipper_length_mm + sex, data = penguins )


# Let's check out the coefficients:
model_2
```

Reference level: 
female = 0,
Adelie penguin species = 0, 
flipper length doesn't have a reference because we only have references for categorical variables

- Explain how we interpret the coefficient 836 "If everything else is held constant, I expect the Gentoo penguin to be 836.26 grams larger than an Adelie penguin"
- "On average, we expect a male penguin to be 530.38 grams larger than a female penguin if everything else is held constant (all other variables are the same)"

## Visualize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~ sex)
```
Males seem to have a larger mass than females on average, in our equation, it says on average, theres 530 grams of increase on average in male penguins compared to female penguins
- does this makes sense? yes
- we can see this difference reflected in our visualization
Does it make sense that Adelie penguins are 836 grams smaller than Gentoo penguins on average? Yes, looking at the graph, yes that makes sense

Similarly, this tells me that on average I would expect that chinstaps would have an 87 gram lower body mass than Adelies, that's a small change, and this is seen in the largely overlapping body masses in our graph











